\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
while saturation is represented in node centered CV basis functions.  Saturation equations are solved explicitly after solving for pressure at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{lux_2012,chen_2006}.

>>>>

Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
while saturation is represented in node centered CV basis functions.  Saturation equations are solved explicitly after solving for pressure at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
